\documentclass[12pt,letterpaper]{article}

\usepackage{mla}
\usepackage{setspace}
\usepackage{calc}

\begin{document}

\begin{mla}{Christopher}{Cooper}{Mrs.~Mills}{English 9 H}{27 October 2012}{An Exploration}

%body here

\singlespacing
\begin{verse}
\parindent=-45pt
\noindent
\hspace{-45pt}I once had thought that life \\
Was a simple thing, \\
A simple thing without strife. 

That day riding along \\
In that nice old car, \\
That nice old car did no wrong. 

Cruising down the freeway \\
The jeep to our left, \\
To our left we saw him sway.

He wanted that exit \\
That was just in front, \\
In front of us he claimed it.

But of us he cared not. \\
He failed to look out, \\
To look out for his blind spot.

And off that road we went \\
Into a dark ditch, \\
A dark ditch of cold dissent.

That stopped my ignorance \\
My lack of tension, \\
Of tension and awful chance.

\hspace{15pt}Before that I had no clue \\
\hspace{15pt}That the world was so askew. \\
\hspace{7pt}I had a picture-perfect view \\
\hspace{15pt}Of a world in fact so blue.

I sometimes sit and think \\
About that old time, \\
that old time, a blissful wink.

But now I am present \\
In a new era, \\
A new era half-pleasant.

Of knowledge, yet knowledge \\
Of horrific things, \\
Horrific things acknowledged.

But bad is not the world \\
Good accompanies, \\
Accompanies with love unfurled.
\end{verse}

\doublespacing


%citations:
%\begin{workscited}
%\bibent
%bibliography entry
%\end{workscited}

\end{mla}

\end{document}
