\documentclass[12pt,letterpaper]{article}

\usepackage{mla13}

\firstname{Sam}
\lastname{Craig}
\professor{Mrs. Mills}
\class{English 9 Honors}
\title{Hard Work and Promotions}

\begin{document}

She left work at five o'clock.
The day seemed odd to her.
She did not remember much of what happened that day.
Most days she could remember a lot, but today little was in her mind.

As she started walking to the bus stop, she thought about how the day went.
It was unlike previous days.
Today her coworkers were a lot more quiet.
Normally the work day is full of having a good time and laughs, but today it was oddly silent.
People were more focused on their work than usual.

At the bus stop, she saw her coworker Bruce Flake.
He normally shared some words with her at the bus stop, even though he did not ride the bus.
She asked him if the day seemed off to him as well.

``People were working harder than usual, but for good reason, right?''  Bruce was referring to the fact that at work today their boss had informed them that a new position was opening up.
They would all be considered for promotion.

``Why would anybody need to act differently for the new opportunity?
If they act differently just for the promotion opportunity, once they get the job they could act how they did before and lose it very easily.''

Bruce shook his head and walked away.
Sandra did not agree with his beliefs, but she got onto the bus to head home.
That evening she was going to eat dinner with her friend Andrea Horton.
Sandra picked up her phone and called her friend.

Andrea did not pick up, so Sandra was forced to leave a message.
Sandra really hoped that Andrea had not forgotten about their dinner, as Sandra enjoyed spending time with Andrea.
Andrea was Sandra's best friend at her workplace, with Bruce being a close second.
A few hours later, Andrea called back.
She had to cancel, which she said was due to too much work that day.
Sandra was upset, but knew that she would be able to talk to her, and all of her coworkers, the next day of work.

Sandra arrived at work, and no one greeted her.
Today was a special day---Wednesday.
On Wednesdays everybody at the workplace went out to lunch together.
They loved to spend the exact moment that the work week became halfway over together.
The idea of this came from Sandra herself.
Many of the workers thought of Sandra as the best organizer of the bunch.

The people of the workplace decided where to go for lunch each Wednesday.
After a few hours of work, Sandra went to the center of the office and asked where people would like to go.

``Sandra, I don't know if today is a good day,'' Bruce said.

``Why in the world would it not be a good day?
It's Wednesday at lunch!'' Sandra exclaimed.

``Work needs to get done.
We all have so much to do.''

``Do people actually agree with Bruce?''
Almost every person in the workplace raised their hands.
Sandra was shocked.
This had been a big tradition for their workplace.
The workers had not missed it even when they had more work than they could handle.
Yet, all of a sudden work mattered more than bonding in the workplace.
Sandra hated this.
She loved spending time with her coworkers, and they were rejecting it.
Sandra sadly walked to Andrea.

``Will you come, Andrea?''
Sandra asked.
Andrea shook her head and explained that she was just as busy with work as everyone else was.

Throughout the rest of the week no coworkers of Sandra's spent time with her.
Their life was work and they toiled with all their might.
Sandra was more upset over this than anything else she had been.
The Monday of the next week, who was getting promoted was to be announced.
Sandra felt as if she had the biggest chance, as she organized the workers at her office the best out of anybody.

It was announced that Bruce Flake and Andrea Horton would be promoted.
Sandra's excitement for them to be promoted far exceeded her disappointment in herself not getting promoted.
She was the most happy for them out of everybody in the workplace.

``Remember to tell me all about the adventures you have in the new workplace!'' Sandra said.
The two promised that they would, and they left with their boss to head to the new workplace.

They never contacted Sandra again.
Interestingly enough, a few weeks later the company was searching for people for the same job once again.

\end{document}
